Data analysis and data transformation

### 2022-07-27 Old/Dag 3 heck.Rmd

>>>>

```{r}
library(tidyverse)
costofliving <- read_csv("https://raw.githubusercontent.com/sbjorkholt/ISSSV1337/main/Week%201/Day%203%20-%20Introduction%20to%20data%20analysis%20and%20data%20transformation/Tasks/costofliving.csv")
```

```{r}
install.packages("janitor")
library(janitor)

costofliving_clean<-costofliving %>%
  clean_names()

## Tidyverse functions

-select
-filter
-mutate
-rename
-group_by
-summarise

### Select

```{r}
costofliving_subset <- costofliving_clean %>%
  select(cost_of_living_index,groceries_index)
```

```{r}
costofliving_clean_subset <- costofliving_clean %>%
  select(cost_of_living_index)
```
```

```{r}
